Report

### 2020-11-24 report.Rmd
Select the model 2 for the follow up

---
title: "Report"
author: "Alain Danet"
date: "`r Sys.Date()`"
tables: yes
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    math: katex
---

@@

@@

```{r, fig.height = 12, fig.width = 12}
log_bm_net_group_f3y %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
  facet_wrap(~variable, scales = "free") +
  labs_log_bm_net_trends()
```

```{r, fig.height = 12, fig.width = 12}
log_bm_net_group_f3y %>%
  filter(!is.na(protocol_type)) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
  facet_grid(variable~protocol_type, scales = "free") +
  labs_log_bm_net_trends()

log_bm_net_group_f3y %>%
  filter(variable == "connectance") %>%
  ggplot(aes(x = bm_slope, y = bm)) +
  geom_point()
  labs(x = "Biomass trends (log biomass per year)", y = "Biomass")
```

@@

```{r}
model_log_bm_f3y_table[["model_obj"]] %>%
  kable(., booktabs = TRUE,
    caption = paste0( "Model summary for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2.")
  )
```

```{r, fig.height = 12, fig.width = 12}
pred_log_bm_quad2 <- summary_log_bm_f3y %>%
  filter(model == "mod_bm_quad2") %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )

pred_log_bm_quad2_plot <- map2(model_log_bm_f3y$data, pred_log_bm_quad2$pred_df,
  plot_pred_data)
legend_quad2 <- get_legend(pred_log_bm_quad2_plot[[1]])
pred_log_bm_quad2_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm_f3y$variable)
plot_grid(top, legend_quad2, rel_widths = c(1, .1))
```

```{r}
effect_quad2_piece <- tibble(
  effect = c("Dynamic of biomass", "disassembly/assembly", "com size", "Effect of bm dyn dep on com size?", "Effect of bm dyn dep on disassembly/assembly context?", "Effect of bm dyn dep on both dis/assembly and com size ?"),
  mod_bm_quad2 = c("bm_slope", "I(bm_slope^2)", "bm", "bm_slope:bm", "I(bm_slope^2)", "bm:I(bm_slope^2)"),
  mod_all_bm = c("bm_slope", "inc_fTRUE", "bm", "bm_slope:bm", "bm_slope:inc_fTRUE", "bm_slope:inc_fTRUE:bm")
)

combin <- expand.grid(
  variable = get_com_str_var(),
  mod_bm_quad2 = unique(effect_quad2_piece$mod_bm_quad2), 
  stat = c("estimate", "p.value")
) %>%
left_join(select(effect_quad2_piece, 2:3)) %>%
pivot_longer(cols = c(mod_bm_quad2, mod_all_bm), names_to = "model", values_to = "term") %>%
mutate_all(as.character)

comparison_table <- distinct(combin) %>%
  mutate(
    coeff = pmap_dbl(list(variable, stat, model, term),
      ~get_coef_from_terms(mydata = model_log_bm_f3y,
	variable = ..1, model = ..3, term = ..4, type = ..2
	) 
  )) %>%
arrange(variable)
unique(comparison_table$term)

test <- comparison_table %>%
  left_join(
    pivot_longer(effect_quad2_piece, cols = c(mod_bm_quad2, mod_all_bm),
      names_to = "model", values_to = "term")
  ) %>%
  select(variable:model, coeff, effect) %>%
  pivot_wider(names_from = stat, values_from = coeff) %>%
  pivot_wider(names_from = model, values_from = c(estimate, p.value))

test2 <- comparison_table %>%
  left_join(
    pivot_longer(effect_quad2_piece, cols = c(mod_bm_quad2, mod_all_bm),
      names_to = "model", values_to = "term")) %>%
  filter(stat == "p.value") %>%
  select(variable:model, coeff, effect) %>%
  pivot_wider(names_from = stat, values_from = coeff) %>%
  pivot_wider(names_from = model, values_from = c(p.value)) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Comparison of the two Statistical model"
    )
  ) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

>>>>

---
title: "Report"
author: "Alain Danet"
self_contained: yes
date: "`r Sys.Date()`"
tables: yes
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    math: katex
---

@@

## The three model

1. $dN = dB + dB \times B + dB^2 + dB^2 \times B$

2. $dN = dB + B + dB \times B + Inc \times B + dB \times Inc \times B$

3. $dN = dB + B + dB \times B + Inc + Inc \times dB + dB \times B \times Inc$

with:
- $dN$: temporal trend of network structure
- $dB$: temporal trend of total (log) biomass
- $B$: total median biomass or total biomass of the first three year
- $Inc$: Is $dB > 0$?

@@

```{r, fig.height = 12, fig.width = 12}
pred_log_bm_quad2 <- summary_log_bm_f3y %>%
  filter(model == "mod_bm_quad2", variable %in% get_com_str_var()) %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    plot_data = map(pred, ~plot(.x, add.data = TRUE)),
    #myplot = map2(pred, data, ~plot_final_model(ggpred = .x, rawdata = .y))
  )
pred_log_bm_quad2_plot <- map2(
  filter(model_log_bm_f3y, variable %in% get_com_str_var())$data,
  pred_log_bm_quad2$pred_df,
  plot_pred_data)
legend_quad2 <- get_legend(pred_log_bm_quad2_plot[[1]])
pred_log_bm_quad2_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm_f3y$variable)
quad2_plot <- plot_grid(top, legend_quad2, rel_widths = c(1, .1))
```

```{r}
pred_log_bm_medium <- summary_log_bm_f3y %>%
  filter(model == "mod_medium_bm", variable %in% get_com_str_var()) %>%
  mutate(
    pred = map(model_obj, ~ggpredict(.x,
	terms = c("bm_slope [-0.2,-0.00001,0.00001,.2]", "inc_f", "bm [quart2]"))),
    pred_df = map(pred, as_tibble),
    plot = map(pred, ~plot(.x, add.data = FALSE)),
    #myplot = map2(pred, , ~plot_final_model(ggpred = .x))
  )
plot_inc <- map2(
  pred_log_bm_medium$pred,
  filter(model_log_bm_f3y, variable %in% get_com_str_var())$data,
  ~plot_final_model(ggpred = .x, rawdata = .y))

plot_inc %<>% map(., ~.x + theme(legend.position = "none"))
medium_plot <- plot_grid(plotlist = plot_inc, labels = pred_log_bm_medium$variable)
```

```{r, fig.height = 12}
plot_grid(quad2_plot, medium_plot, nrow = 2, labels = c("poly", "piecereg"))
```

```{r}
loadd(model_log_bm, summary_model_log_bm,
  summary_log_bm, vif_model_log_bm)
```

```{r}
effect_quad2_piece <- tibble(
  effect = c("Dynamic of biomass", "disassembly/assembly", "com size", "bm dyn dep on com size?", "bm dyn dep on disassembly/assembly?", "bm dyn dep on both dis/assembly and com size ?"),
  mod_bm_quad2 = c("bm_slope", "I(bm_slope^2)", "bm", "bm_slope:bm", "I(bm_slope^2)", "bm:I(bm_slope^2)"),
  mod_medium_bm = c("bm_slope", "bm_slope:inc_fTRUE", "bm", "bm_slope:bm", "bm_slope:inc_fTRUE", "bm_slope:bm:inc_fTRUE")
)
effect_quad2_piece %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Hypothesis and matching coefficients."
    )
    )
```

```{r}
hyp_table_f3y <- make_hyp_table(hyp_table = effect_quad2_piece, mod = model_log_bm_f3y)

hyp_table_f3y %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Comparison of the two Statistical model for first three year"
    )
  ) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
hyp_table <- make_hyp_table(hyp_table = effect_quad2_piece, mod = model_log_bm)
hyp_table %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Comparison of the two Statistical model for the median biomass model"
    )
  ) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

```{r}
model_log_bm_f3y_table_medium <- get_table_from_summary(
  .data = summary_log_bm_f3y,
  model =  "mod_medium_bm",
  variable = get_com_str_var(all = FALSE)
)

model_log_bm_f3y_table_medium[["reg_table"]] %>% 
  kable(.,
    booktabs = TRUE, 
    caption = 
      paste0(
      "Regression table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )) %>% 
  kable_styling(latex_options =c("scale_down")) %>%
  #add_header_above(c(" " = 3, "Indirect effects via" = 5)) %>%
  #column_spec(1:2, width = "3cm") %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_bm_f3y_table_medium[["anova_table"]] %>% 
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )
  ) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

```{r, fig.height = 12, fig.width = 12}
log_bm_net_group_f3y %>%
  filter(!is.na(protocol_type)) %>%
  ggplot(aes(x = bm_slope, y = linear_slope, color = log(bm))) +
  geom_point() +
  scale_color_viridis() +
  geom_errorbar(aes(xmin = bm_slope - bm_slope_strd_error,
      xmax = bm_slope + bm_slope_strd_error), alpha = .3) +
  geom_errorbar(aes(ymin = linear_slope - linear_slope_strd_error,
      ymax = linear_slope + linear_slope_strd_error), alpha = .3) +
  facet_grid(variable~protocol_type, scales = "free") +
  labs_log_bm_net_trends()
```
